### 2024-01-31 ms.qmd
Update ms.qmd

```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(i in 1:length(specie)){
  for(j in 1:length(groups)){
    for(k in 1:length(hormone)){
      for(l in 1:length(temperature)){
        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], groups[j], hormone[k], temperature[l])
      }
    }
  }
}
```

@@

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## B) L. delicata
deli_red <- fit_m(clean_df, "deli", "red", refit = TRUE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m(clean_df, "deli", "blue", refit = TRUE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## B) L. guichenoti
guich_red <- fit_m(clean_df, "guich", "red", refit = TRUE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m(clean_df, "guich", "blue", refit = TRUE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
### Group = red
drr_CORTCold <- deli_rev_red$b_trial_reversal
drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
### Group = blue
drb_CORTCold <- deli_rev_blue$b_trial_reversal
drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
## 2) L. guichenoti
### Group = red
grr_CORTCold <- guich_rev_red$b_trial_reversal
grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
### Group = blue
grb_CORTCold <- guich_rev_blue$b_trial_reversal
grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
```

@@

groups <- c("Red", "Blue")
test <- c("Associative", "Reversal")

@@

estimates_asso <- list(
  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot, 
  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot, 
  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot

@@

estimates_rev <- list(
  drr_CORTCold, drr_ControlCold, drr_CORTHot, drr_ControlHot, 
  drb_CORTCold, drb_ControlCold, drb_CORTHot, drb_ControlHot, 
  grr_CORTCold, grr_ControlCold, grr_CORTHot, grr_ControlHot, 
  grb_CORTCold, grb_ControlCold, grb_CORTHot, grb_ControlHot

@@

asso_mean <- format_dec(sapply(estimates_asso, mean), 3)
asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
asso_interval_975 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.975)), 3)
asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 3)
rev_mean <- format_dec(sapply(estimates_rev, mean), 3)
rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
rev_interval_975 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.975)), 3)
rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 3)
# Building the df for the associative
asso_df <- data.frame(
  Specie = rep(specie, each = length(groups) * length(treatments)),
  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
  Mean = rep(asso_mean, each = 1),
  CI = rep(asso_intervals, each = 1),
  PValue = rep(asso_pvalue, each = 1),
  Task = rep("Associative", length(asso_mean))
# Building the df for the reversal
rev_df <- data.frame(
  Specie = rep(specie, each = length(groups) * length(treatments)),
  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
  Mean = rep(rev_mean, each = 1),
  CI = rep(rev_intervals, each = 1),
  PValue = rep(rev_pvalue, each = 1),
  Task = rep("Reversal", length(rev_mean))
# Joining both dfs
table_data <- rbind(asso_df, rev_df)
table_data[, sapply(table_data, is.numeric)] <- lapply(table_data[, sapply(table_data, is.numeric)], function(x) format(x, scientific = FALSE))

@@

  separate(model, into = c("Specie", "Group", "cort", "temp"), sep = "_") %>%

@@

new_table_data <- merge(table_data, n_df) %>%

@@

  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #To order the columns in the way I want for the table

@@

        Group = factor(Group,
                  levels = c("Red", "Blue")),

@@

  arrange(Specie, Group, Treatment) %>% # To arrange the rows the way I want

@@

In the reversal tesk, we decided to pool both groups 'Blue' and 'Red' to make the between-treatment comparisons for two reasons. First, we did not find any significant differences caused group on the learning slopes (_L. delicata_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`, p = `r format_dec(pmcmc((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`; _L. guichenoti_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`, p = `r format_dec(pmcmc((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`). Second, we were expecting an acquired bias towards the colour assigned in the associative task as part of the design. Nonetheless, we did not find any significant differences between treatments in _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`) (see @Figguich). We did not find any effect of incubation temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled. Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).

>>>>

```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(i in 1:length(specie)){
  for(k in 1:length(hormone)){
    for(l in 1:length(temperature)){
      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
      }
    }
  }
```

@@

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## A) L. delicata
deli <- fit_m(clean_df, "deli", refit = TRUE)
write.csv(deli, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich <- fit_m(clean_df, "guich", refit = TRUE)
write.csv(guich, file= "./output/Checking/guich.csv")
```

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
deli_CORTCold <- deli$b_trial_reversal
deli_ControlCold <- (deli$'b_trial_reversal:cortControl' + deli$b_trial_reversal)
deli_CORTHot <- (deli$'b_trial_reversal:tempHot' + deli$b_trial_reversal)
deli_ControlHot <- (deli$'b_trial_reversal:cortControl:tempHot' + deli$b_trial_reversal + deli$'b_trial_reversal:cortControl' + deli$'b_trial_reversal:tempHot')
## 2) L. guichenoti
guich_CORTCold <- guich$b_trial_reversal
guich_ControlCold <- (guich$'b_trial_reversal:cortControl' + guich$b_trial_reversal)
guich_CORTHot <- (guich$'b_trial_reversal:tempHot' + guich$b_trial_reversal)
guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_trial_reversal + guich$'b_trial_reversal:cortControl' + guich$'b_trial_reversal:tempHot')
```

@@

@@

estimates <- list(
  deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot, 
  guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot

@@

mean <- format_dec(sapply(estimates, mean), 3)
interval_025 <- format_dec(sapply(estimates, function(x) quantile(x,0.025)), 3)
interval_975 <- format_dec(sapply(estimates, function(x) quantile(x,0.975)), 3)
intervals <- paste(interval_025, interval_975, sep = " , ")
pvalue <- format_dec(sapply(estimates, pmcmc), 3)
# Building the df
table_df <- data.frame(
  Specie = rep(specie, each = length(treatments)),
  Treatment = rep(rep(treatments, each = 1), times = length(specie)),
  Mean = rep(mean, each = 1),
  CI = rep(intervals, each = 1),
  PValue = rep(pvalue, each = 1),

@@

@@

  separate(model, into = c("Specie", "cort", "temp"), sep = "_") %>%

@@

new_table_df <- merge(table_df, n_df) %>%

@@

  select(Specie, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table

@@

@@

  arrange(Specie, Treatment) %>% # To arrange the rows the way I want

@@

We did not find any significant differences between treatments in _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((deli_ControlHot + drb_ControlHot) - (deli_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((deli_ControlHot + drb_ControlHot) - (deli_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((deli_ControlHot + drb_ControlHot) - (deli_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlHot + drb_ControlHot) - (deli_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((deli_CORTHot + drb_CORTHot) - (deli_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + drb_CORTHot) - (deli_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((guich_ControlCold + grb_ControlCold) - (guich_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((guich_ControlCold + grb_ControlCold) - (guich_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((guich_ControlHot + grb_ControlHot) - (guich_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((guich_ControlHot + grb_ControlHot) - (guich_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((guich_ControlHot + grb_ControlHot) - (guich_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlHot + grb_ControlHot) - (guich_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((guich_CORTHot + grb_CORTHot) - (guich_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + grb_CORTHot) - (guich_CORTCold + grb_CORTCold)), 3)`) (see @Figguich). We did not find any effect of incubation temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot + drb_CORTHot + drb_ControlHot) - (deli_CORTCold + deli_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot + drb_CORTHot + drb_ControlHot) - (deli_CORTCold + deli_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot + grb_CORTHot + grb_ControlHot) -(guich_CORTCold + guich_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot + grb_CORTHot + grb_ControlHot) -(guich_CORTCold + guich_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot + drb_ControlCold + drb_ControlHot) - (deli_CORTCold + deli_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot + drb_ControlCold + drb_ControlHot) - (deli_CORTCold + deli_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot + grb_ControlCold + grb_ControlHot)-(guich_CORTCold + guich_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot + grb_ControlCold + grb_ControlHot)-(guich_CORTCold + guich_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled. Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).
